Corpus Stats

### 2019-03-19 notebooks/corpus_stats_and_plots.Rmd
got plots working, need to sort out the many many points. but the sorting is there

Similar to the R stuff.
Now, we should combine these plots.
```{r}
combo_df <- r_c_df
combo_df$loc_c <- c_c_df$loc_c
combo_df$loc_r <- sapply(combo_df$loc_r, function(x) if (x == 0) x else log10(x))
combo_df$loc_c <- sapply(combo_df$loc_c, function(x) if (x == 0) x else log10(x))

# sort
combo_df <- combo_df[order(combo_df$loc_r), ]

# TODO: not staying sorted, probably id.vars
zzz <- melt(combo_df, id.vars="package_name", variable.name = "language")

@@

@@

# plot it
plot_both
```

>>>>

Similar to the R stuff.
Now, we should combine these plots.
Messy graphs, beware!
```{r}
combo_df <- r_c_df
combo_df$loc_c <- c_c_df$loc_c
combo_df$loc_r <- sapply(combo_df$loc_r, function(x) if (x == 0) x else log10(x))
combo_df$loc_c <- sapply(combo_df$loc_c, function(x) if (x == 0) x else log10(x))

# sort
combo_df <- combo_df[order(combo_df$loc_r), ]
# this makes sure the package_names are in the right order, ggplot2 plots according to factors
# and levels
combo_df$package_name <- factor(combo_df$package_name, levels=combo_df$package_name)

combo_df_c <- combo_df[order(combo_df$loc_c), ]
combo_df_c$package_name <- factor(combo_df_c$package_name, levels=combo_df_c$package_name)

combo_df_c <- combo_df_c[combo_df_c$loc_c > 0, ]

# TODO: not staying sorted, probably id.vars
zzz <- melt(combo_df, id.vars="package_name", variable.name = "language")
zzz_c <- melt(combo_df_c, id.vars="package_name", variable.name = "language")

@@

plot_both_c <- ggplot( data=zzz_c, aes(package_name, value, group=1))
plot_both_c <- plot_both_c + geom_line(aes(colour = language)) + geom_point(aes(colour = language))
plot_both_c <- plot_both_c + labs(
  title = "Analysis of R Corpus (R and C)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of Code in Package (Log10-scaled)"
)

@@

plot_both_c <- plot_both_c + theme(axis.text.x = element_blank())

# plot it
plot_both

plot_both_c
```
